Scientific Report - Summary of Research\\ Ambizione: ``Automatized compilation of sequential software to a diverse set of hardware accelerators''\\ Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
deploy: 526e7bc303288efc892c17c9db77d3a9497bc084

The central compnents of this library have already been upstreamed into the
open-source LLVM/MLIR project and are usable by the wider research and 
industrial community.

>>>>

The central components of this library have already been upstreamed into the
open-source LLVM/MLIR project and are usable by the wider research and 
industrial community.
